### 2021-11-09 papers/thesis/resubmitted/acknowledgements/acknowledgements.tex
Actually, spotted typo in EPSRC. Fixed.

Firstly, I would like to express my thanks to ESPRC for their financial support, and to the Mathematics of Planet Earth Centre for Doctoral Training (MPE CDT) for providing me with the incredible opportunities that the course has brought.

>>>>

Firstly, I would like to express my thanks to EPSRC for their financial support, and to the Mathematics of Planet Earth Centre for Doctoral Training (MPE CDT) for providing me with the incredible opportunities that the course has brought.
